**fabryka**

### 2025-07-14 fabryka_pci/article.Rmd
correction of fabryka shiny application and description article after first round of review in PCI archaeology

-   source code: <https://github.com/marchaeologist/fabryka/tree/main> \smallbreak
-   Report bugs or any request: <https://github.com/marchaeologist/fabryka/issues> \smallbreak
-   github reprository doi of fabryka:
    <https://doi.org/10.5281/zenodo.15207419> \smallbreak
-   Zenodo repository of this article:
    <https://doi.org/10.5281/zenodo.15236695> \bigbreak

>>>>

-   source code: <https://github.com/marchaeologist/fabryka/tree/main> \smallbreak
-   Report bugs or any request: <https://github.com/marchaeologist/fabryka/issues> \smallbreak
-   github reprository doi of fabryka:
    <https://doi.org/10.5281/zenodo.15207419> \smallbreak
-   Zenodo repository of this article:
    <https://doi.org/10.5281/zenodo.15879462> \bigbreak
